---
title: "Tracker Radar Exploration"
output: html_notebook
---

This is an [Tracker Radar](https://spreadprivacy.com/duckduckgo-tracker-radar/) data set from DuckDuckGo. The [data model is documented on Github](https://github.com/duckduckgo/tracker-radar/blob/master/docs/DATA_MODEL.md).

## Setup

```{r setup}

library(tidyverse)
library(scales)
library(jsonlite)
library(patchwork)

theme_bar <- theme_minimal() +
  theme(plot.title.position = "plot",
        plot.title = element_text(size = 14, face = "bold", color = "gray10"),
        plot.subtitle = element_text(size = 12, face = "italic", 
                                     margin = margin(0, 0, 12, 0, "pt")),
        plot.caption = element_text(face = "italic", size = 11, lineheight = 1.1, color = "gray40"),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12), 
        panel.grid = element_blank(),
        panel.spacing = unit(1, "lines"),
        strip.text = element_text(size = 12, face = "bold", vjust = 1, hjust = 0),
        strip.text.y.left = element_text(angle = 0),
        strip.placement = "outside")

```

## Load Up the Data

Domain data included:

* **Prevalence** – The percentage of the sites in DuckDuckGo's crawl that request this third-party domain.
* **Sites** – The actual count of sites this domain was found on in DuckDuckGo's crawl.
* **Categories** – High-level reasons for using this domain as a third party.
* **Fingerprinting** – How likely this domain is to be using fingerprinting techniques as a third party: 
0 = no use of browser APIs
1 = some use of browser APIs, but not obviously for tracking purposes
2 = use of many browser APIs, possibly for tracking purposes
3 = excessive use of browser APIs, almost certainly for tracking purposes
* **Cookies** – The percentage of the sites in DuckDuckGo's crawl that have cookies set by this third-party domain.
* **Performance** – Impact of loading resources from this domain. Each of these fields is assigned a value from 1-3, where 1 is little to no performance impact, and 3 is high impact. The delta between values representing an order of magnitude difference.
* **Owner** – Parent entity.
* **Resources** – Scripts, pixels, and other common resources this domain uses.
* **Subdomains** – Subdomains these resources may be found on.

```{r load_data}

domain_list <- list.files("domains")

get_domain_data <- function(domain_name){
  
  # cat(domain_name, "\n")
  
  # Read in the File
  domain_data <- read_json(paste0("domains/", domain_name))
  
  # Extract data from the JSOn
  df <- data.frame(domain = domain_data$domain,
                   owner = ifelse(is.null(domain_data$owner$displayName), 
                                  NA, domain_data$owner$displayName),
                   prevalence = domain_data$prevalence,
                   sites = domain_data$sites,
                   fingerprinting = domain_data$fingerprinting,
                   cookies = domain_data$cookies,
                   performance_time = ifelse(is.null(domain_data$performance$time),
                                             NA, domain_data$performance$time),
                   performance_size = ifelse(is.null(domain_data$performance$size),
                                             NA, domain_data$performance$size),
                   performance_cpu = ifelse(is.null(domain_data$performance$cpu),
                                            NA, domain_data$performance$cpu),
                   performance_cache = ifelse(is.null(domain_data$performance$cache),
                                              NA, domain_data$performance$cache),
                   stringsAsFactors = FALSE)
  
  # Get the number of categories
  num_categories <- unlist(domain_data$categories) %>% length()
  
  # Create one row for each category, repeating all of the above information
  if(num_categories == 0){
    df$categories <- "Uncategorized"
  } else {
    df <- df %>% uncount(num_categories)
    df$categories <- unlist(domain_data$categories)
  }
  
  # Return the data frame
  df
}

# Get the data for all of the files
domain_data <- map_dfr(domain_list, get_domain_data)

```

## What are the most prevalent domains?

```{r most prevalent}

most_prevalent <- domain_data %>% select(-categories) %>% 
  distinct() %>% arrange(-prevalence)

head(most_prevalent, 25)

```

## What Types (Categories) of Trackers Were Captured?

```{r cat_num, fig.height = 6, echo = FALSE}

# Get the number of domains for each category and build a plot
domains_with_categories <- domain_data %>% 
  filter(categories != "Uncategorized") %>% 
  group_by(categories) %>% summarise(n = n()) %>% 
  arrange(n) 

# Need this for the next section: top 5 categories
top_5_cats <- top_n(domains_with_categories, 5, n) %>% arrange(-n)

domains_with_categories$categories <- factor(domains_with_categories$categories, 
                                             levels = domains_with_categories$categories)

uncat <- domain_data %>% filter(categories == "Uncategorized") %>% nrow()

gg_domain_w_categories <- ggplot(domains_with_categories, aes(x = categories, y = n, label = format(n, big.mark = ","))) + 
  geom_bar(stat = "identity", fill = "#58b792") + 
  geom_hline(aes(yintercept = 0)) +
  geom_text(aes(y = n + 2), hjust = 0, size = 4, color = "gray40") +
  
  scale_y_continuous(limits = c(0, 400), expand = c(0,0)) +
  labs(title = "Number of Detected Third Party Domains by Category",
       subtitle = paste0("(", format(uncat, big.mark = ","), " Uncategorized Domains Not Shown)"),
       caption = "Source: DuckDuckGo Tracker Radar\nCategory Descriptions: http://bit.ly/tr-categories") +
  coord_flip() +
  theme_bar


# Get the top 5 domains for each of the top 5 categories and show their prevalence  
top_by_category <- domain_data %>% 
  filter(categories %in% top_5_cats$categories) %>% 
  mutate(categories = ifelse(categories == "Ad Motivated Tracking", "Ad Motivated\nTracking",
                             ifelse(categories == "Audience Measurement", "Audience\nMeasurement",
                                    ifelse(categories == "Third-Party Analytics Marketing", 
                                           "Third-Party\nAnalytics Marketing", categories)))) %>% 
  group_by(categories) %>% top_n(5, prevalence) %>% ungroup() %>%  
  arrange(categories, prevalence) %>% 
  # This is for ordering things as we'd like
  # See: https://drsimonj.svbtle.com/ordering-categories-within-ggplot2-facets
  mutate(order = row_number()) %>% 
  select(order, categories, domain, owner, prevalence, fingerprinting, cookies) %>% 
  # Make a unique key that we can then turn into a factor to control the ordering
  mutate(domain_cat = paste0(domain, "|", categories)) %>% 
  mutate(domain_cat = factor(domain_cat))

gg_top_by_cat <- ggplot(top_by_category, aes(x = order, y = prevalence, label = percent(prevalence, 0.1))) +
  geom_bar(stat = "identity", fill = "#678fff") +
  geom_text(mapping = aes(y = prevalence + .04), size = 4, color = "gray40") +
  scale_y_continuous(expand = c(0,0), limits = c(0, max(top_by_category$prevalence + 0.12))) +
  # Add categories to axis
  scale_x_continuous(breaks = top_by_category$order, labels = top_by_category$domain, expand = c(0,0)) +
  labs(title = "Prevalence of the Top 5 Domains in the Top 5 Categories",
       subtitle = "Prevalence = The % of the ~43,000 Inspected Sites on Which the 3rd Party Domain Was Found",
       caption = "Source: DuckDuckGo Tracker Radar") +
  
  facet_grid(rows = vars(categories), scales = "free_y", switch = "y") +
  # facet_wrap(~ categories, scales = "free") +
  coord_flip() + 
  theme_bar

gg_domain_w_categories
gg_top_by_cat


```



```

